An introduction to wavelets using R

### 2022-01-11 text/14/wavelets.Rmd
Started inverse wavelet transform on wavelets.md

```{r graphing-functions}
graph_with_axis <- function(x, lab, limits=range(x)) {
  par(mar=c(2.6, 0, 0, 0))
  plot((1:2048)/2048, x, 
       xlim=c(0, 1.2), 
       ylim=limits, 
       type="l",
       axes=FALSE)
  axis(side=1, at=(0:4)/4, labels=c(1, 512, 1024, 1536, 2048))
  text(1.1, x[2048], lab, adj=0.5)
}
graph_without_axis <- function(x, lab, limits=range(x)) {
  par(mar=c(0, 0, 0, 0))
  plot((1:2048)/2048, x, 
       xlim=c(0, 1.2), 
       ylim=limits, 
       type="l",
       axes=FALSE)
  text(1.1, x[2048], lab, adj=0.5)
}
needle_plot <- function(y, lab, x=seq(0, 1, along.with=y)) {
  par(mar=c(0, 0, 0, 0))
  plot(
    x, y, 
    xlim=c(0, 1.2), 
    type="n",
    axes=FALSE)
  segments(x, 0, x, y)
  text(1.1, 0, lab)
}
```

@@

```{r first-level-wavelet}
wt.1 <- mdwt(ecg, g, L=1)
V1 <- wt.1$y[   1:1024]
W1 <- wt.1$y[1025:2048]
{
  needle_plot(V1, "V1")
  needle_plot(W1, "W1")
  graph_without_axis(ecg, "Original\nsignal")
}
```

@@

```{r second-level-wavelet}
wt.2 <- mdwt(ecg, g, L=2)
V2 <- wt.2$y[1:512]
W2 <- wt.2$y[513:1024]
quality_check_W1 <- wt.2$y[1025:2048]
all(quality_check_W1==W1)
{
  needle_plot(V2, "V2")
  needle_plot(W2, "W2")
  needle_plot(W1, "W1")
  graph_without_axis(ecg, "Original\nsignal")
}
```

@@

```{r third-level-wavelet}
wt.3 <- mdwt(ecg, g, L=3)
V3 <- wt.3$y[1:256]
W3 <- wt.3$y[257:512]
W2_check3 <- wt.3$y[513:1024]
W1_check3 <- wt.3$y[1025:2048]
all(W2_check3==W2)
all(W1_check3==W1)
{
  needle_plot(V3, "V3")
  needle_plot(W3, "W3")
  needle_plot(W2, "W2")
  needle_plot(W1, "W1")
  graph_without_axis(ecg, "Original\nsignal")
}
```

@@

```{r ninth-level-wavelet}
wt.9 <- mdwt(ecg, g, L=9)
V9 <- wt.9$y[   1:   4]
W9 <- wt.9$y[   5:   8]
W8 <- wt.9$y[   9:  16]
W7 <- wt.9$y[  17:  32]
W6 <- wt.9$y[  33:  64]
W5 <- wt.9$y[  65: 128]
W4 <- wt.9$y[ 129: 256]
W3 <- wt.9$y[ 257: 512]
W2 <- wt.9$y[ 513:1024]
W1 <- wt.9$y[1025:2048]
{
  needle_plot(V9, "V9")
  needle_plot(W9, "W9")
  needle_plot(W8, "W8")
  needle_plot(W7, "W7")
  needle_plot(W6, "W6")
  needle_plot(W5, "W5")
  needle_plot(W4, "W4")
  needle_plot(W3, "W3")
  needle_plot(W2, "W2")
  needle_plot(W1, "W1")
  graph_without_axis(ecg, "Original\nsignal")
}
```

```{r}
level_wavelet <- function(wt.rwt, i) {
  v <-wt.rwt$y
  v[(2^(i-1)):(2^i)] <- 0
  as.vector(midwt(v, d4.rwt$h.0, L=9)$x)
}
```

@@

c(V8[1], rev(h) %*% V9_diluted[1:4] + rev(g) %*% W9_diluted[1:4])
c(V8[2], rev(h) %*% V9_diluted[2:5] + rev(g) %*% W9_diluted[2:5])
```

>>>>

```{r graphing-functions}
graph_with_axis <- function(x, lab, limits=range(x)) {
  par(mar=c(2.6, 0, 0, 0))
  plot((1:2048)/2048, x, 
       xlim=c(0, 1.2), 
       ylim=limits, 
       type="l",
       axes=FALSE)
  axis(side=1, at=(0:4)/4, labels=c(1, 512, 1024, 1536, 2048))
  text(1.1, x[2048], lab, adj=0.5)
}
graph_without_axis <- function(x, lab, limits=range(x)) {
  par(mar=c(0, 0, 0, 0))
  plot((1:2048)/2048, x, 
       xlim=c(0, 1.2), 
       ylim=limits, 
       type="l",
       axes=FALSE)
  text(1.1, x[2048], lab, adj=0.5)
}
needle_plot <- function(y, lab, x=seq(0, 1, along.with=y), limits=range(y)) {
  par(mar=c(0, 0, 0, 0))
  plot(
    x, y, 
    xlim=c(0, 1.2), 
    ylim=limits,
    type="n",
    axes=FALSE)
  segments(x, 0, x, y)
  text(1.1, 0, lab)
}
```

@@

```{r first-level-wavelet}
wt.1 <- mdwt(ecg, g, L=1)
V1 <- wt.1$y[   1:1024]
W1 <- wt.1$y[1025:2048]
{
  needle_plot(V1, "V1", limits=range(ecg))
  needle_plot(W1, "W1", limits=range(ecg))
  graph_without_axis(ecg, "Original\nsignal", limits=range(ecg))
}
```

@@

```{r second-level-wavelet}
wt.2 <- mdwt(ecg, g, L=2)
V2 <- wt.2$y[1:512]
W2 <- wt.2$y[513:1024]
quality_check_W1 <- wt.2$y[1025:2048]
all(quality_check_W1==W1)
{
  needle_plot(V2, "V2", limits=range(ecg))
  needle_plot(W2, "W2", limits=range(ecg))
  needle_plot(W1, "W1", limits=range(ecg))
  graph_without_axis(ecg, "Original\nsignal", limits=range(ecg))
}
```

@@

```{r third-level-wavelet}
wt.3 <- mdwt(ecg, g, L=3)
V3 <- wt.3$y[1:256]
W3 <- wt.3$y[257:512]
W2_check3 <- wt.3$y[513:1024]
W1_check3 <- wt.3$y[1025:2048]
all(W2_check3==W2)
all(W1_check3==W1)
{
  needle_plot(V3, "V3", limits=range(ecg))
  needle_plot(W3, "W3", limits=range(ecg))
  needle_plot(W2, "W2", limits=range(ecg))
  needle_plot(W1, "W1", limits=range(ecg))
  graph_without_axis(ecg, "Original\nsignal", limits=range(ecg))
}
```

@@

```{r ninth-level-wavelet}
wt.9 <- mdwt(ecg, g, L=9)
V9 <- wt.9$y[   1:   4]
W9 <- wt.9$y[   5:   8]
W8 <- wt.9$y[   9:  16]
W7 <- wt.9$y[  17:  32]
W6 <- wt.9$y[  33:  64]
W5 <- wt.9$y[  65: 128]
W4 <- wt.9$y[ 129: 256]
W3 <- wt.9$y[ 257: 512]
W2 <- wt.9$y[ 513:1024]
W1 <- wt.9$y[1025:2048]
{
  needle_plot(V9, "V9", limits=range(ecg))
  needle_plot(W9, "W9", limits=range(ecg))
  needle_plot(W8, "W8", limits=range(ecg))
  needle_plot(W7, "W7", limits=range(ecg))
  needle_plot(W6, "W6", limits=range(ecg))
  needle_plot(W5, "W5", limits=range(ecg))
  needle_plot(W4, "W4", limits=range(ecg))
  needle_plot(W3, "W3", limits=range(ecg))
  needle_plot(W2, "W2", limits=range(ecg))
  needle_plot(W1, "W1", limits=range(ecg))
  graph_without_axis(ecg, "Original\nsignal", limits=range(ecg))
}
```

@@

c(V8[1], rev(h) %*% V9_diluted[1:4] + rev(g) %*% W9_diluted[1:4])
c(V8[2], rev(h) %*% V9_diluted[2:5] + rev(g) %*% W9_diluted[2:5])
V9_coefficients <- rep(0, 2048)
V9_coefficients[1:8] <- wt.9$y[1:8]
V9_signal <- as.vector(midwt(V9_coefficients, d4.rwt$h.0, L=9)$x)
{
  graph_without_axis(V9_signal, "V9", limits=range(ecg))
  graph_without_axis(ecg, "Original\nsignal", limits=range(ecg))
}
```
